Done

### 2025-01-07 done.qmd
update

@@

2012: [The Cognitive Science Safari](https://sites.google.com/d/1nQb4g6jqk7M0gwaD4Bvw7QKtBg0nkQRV/p/1Q0M0b1kRUveC9w0Li7Je0A1f1E8PzzYB/edit) was a street-tour of classic social psychology experiments, in Berlin as part of the BMW Guggenheim Lab.

>>>>

2012 September: [The Cognitive Science Safari](done/2012-09-06.html) was a street-tour of classic social psychology experiments, in Berlin as part of the BMW Guggenheim Lab. I was on the cover of the Wall Street Journal.

@@
